Dynamics of thin liquid film flows studied with the lattice Boltzmann method

### 2023-07-11 chapters/Method.tex
Minor changes

Coming up in this chapter is a short overview of numerical methods to simulate the thin film equation.
Starting with the straightforward finite differences approach and an introduction of the CFL criteria.
But also introducing the bottom up approach where Newtons equation of motion is solved for every molecule.
Followed by an short introduction to the main method of this work, the lattice Boltzmann method~\cite{PhysRevLett.56.1505, krueger2017, succi}. 
The mathematical framework as well as it's link to kinetic theory will be discussed and the idea of the Chapmann-Enskog expansion will be outlined~\cite{Chapman, Enskog}. 
Based on the mathematical model it is possible to define a numerical approach.
Using assumptions, mainly concerning the collision operator, the resulting algorithm is fairly easy to implement and shows good scalability.
Which closes the loop with the above statement that the resulting source code is a perfect candidate for GPU programming.

@@

\section{The Lattice Boltzmann Method}\label{sec:LBM}
\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{graphics/Scales_problem.pdf}
    \caption{Schematic display of how different approaches relate to different length and time scales.
    The finer the system is resolved the more computing resources are needed.}
    \label{fig:scales_dummy}
\end{figure}
The lattice Boltzmann method is as the name suggests a discretization approach to the Boltzmann equation~\cite{krueger2017, succi, wolf-gladrow}.
Boltzmann more then a hundred years ago introduced a model that was build on the assumptions that atoms and molecules move classically.
This was actually just a small portion of his groundbreaking work which forms a whole subsection of physics called statistical mechanics. 
He as well knew that there are a lot of oxygen, nitrogen and other atoms that make up the content of air we inhale with a single breath.
In 1811 already Avogadro calculated that rough number of molecules and around fifty years later Loschmidt came to a similar result~\cite{avogadro1811essai, loschmidt52grosse}
\begin{equation}
    n = \frac{p N_A}{R T},
\end{equation}
where $n$ is the number density, $p$ the pressure, $R$ the gas constant and $T$ the temperature.
The constant named after Avogadro ($N_A$) states that a mole of some substance has about $6 \cdot 10^{23}$ atoms.
Boltzmanns ingenious idea, this adjective is justified as even mathematicians find statistical mechanics appealing, to solve the dynamics of this complex coupled system was to use an statistical ansatz.
Instead of solving the equations of motion for every particle, which is the idea of molecular dynamics as introduced above, Boltzmann decided to introduce distribution functions $f(\mathbf{x},{\boldsymbol\xi},t)$, which depend on position, momentum and time and generate an ensemble.
Figure~\ref{fig:scales_dummy} illustrates the idea coming from either a macroscopic system or a microscopic system.
Instead of dealing with every atom or molecule, which is displayed in the bottom left of the figure, it is also possible to use a more coarse approach. 
Which is shown in the middle of the figure where distributions over ensembles of particles are used~\cite{raabe2004overview}.
Therefore instead of working in the microscopic world the lattice Boltzmann method works in a mesoscopic regime.
Making it computationally more efficient for larger class of problems.
Of course, it is also possible to use a coarser approach and in fact a lot of the classical Navier-Stokes solvers operate in the upper right of Fig.~\ref{fig:scales_dummy}, see Chap.~\ref{chapter:fourth_paper} for some example solvers.

\subsection{The Boltzmann equation}
The dynamics of this distributions $f$ can be formalized and put into an evolution equation which is called the Boltzmann equation
\begin{equation}\label{eq:boltzmann_eq}
    \partial_t f + {\boldsymbol\xi}\cdot\nabla f + \frac{1}{\rho}\mathbf{F}\cdot\partial_{{\boldsymbol\xi}}f = \Omega(f), 
\end{equation}
where ${\boldsymbol\xi}$ is the momentum and the first two terms describe the advection of the distribution due to the atoms and the third term measures the effect of a force $\mathbf{F}$ on the momentum~\cite{krueger2017}.
On the right side of the equation is an arbitrary complex term, the collision operator.
This operator accounts for all collisions the atoms or particles perform at any given instance of time.
In principle this operator can not be computed analytically, because one need to integrate out the whole phase space $(\int \diff^3\mathbf{x}, \int \diff^3\xi)$ for all possible collision terms, therefore for the two up to n-point interactions.

However with a smart ansatz it is possible to find a suitable approximation to the collision operator.
The easiest ansatz one can make is
\begin{enumerate}
    \item The fluids state is not far of its equilibrium.
    \item During the collision it approaches its equilibrium with a relaxation time $\tau$.
\end{enumerate}
Bhatnagar, Gross and Krook (BGK) were the first ones who worked out the mathematical model behind this ansatz~\cite{PhysRev.94.511}.
This model can be formalized quite simply and reads
\begin{equation}
    \Omega(f) = -\frac{1}{\tau}(f - f^{eq}),
\end{equation}
where $f^{eq}$ denotes the equilibrium distribution function.
The moments of the BGK collision operator satisfy the following set of equations
\begin{align}
    \int \Omega(f) \diff^3\xi = 0, \label{eq:BGK_1}\\
    \int {\boldsymbol\xi}\Omega(f) \diff^3\xi = \mathbf{0}, \label{eq:BGK_2}\\
    \int |{\boldsymbol\xi}|^2\Omega(f) \diff^3\xi = 0, \label{eq:BGK_3}\\
    \int |\mathbf{v}|^2\Omega(f) \diff^3\xi = 0. \label{eq:BGK_4}
\end{align}
The first of the above equations states that the mass is conserved, while Eq.~(\ref{eq:BGK_2}) ensures momentum conservation.
Eqs.~(\ref{eq:BGK_3}, \ref{eq:BGK_4}) tell us that both that the total energy as well as the internal energy are conserved.
Taking this four constraints into consideration as well as the points 1. and 2. one finds that the BGK operator is the simplest one to satisfy them all.
With one side note however, the full collision operator from Boltzmann does predict a different Prandtl number ($Pr$) than the BGK yields.
The Prandtl number $Pr = \nu/\alpha$ measures viscosity against thermal diffusivity ($\alpha$). 
Using BGK one gets $Pr=1$ while monoatomic gases or Boltzmann's operator showing $Pr\simeq 2/3$~\cite{cercignani1988boltzmann, krueger2017}.

@@

Performing a Taylor expansion of Eq.~(\ref{eq:boltzmann_eq}) with a discrete set of velocities assuming no force is present yields~\cite{krueger2017}
\begin{equation}\label{eq:Taylor_discret_boltzmann}
    \Delta t (\partial_t + c_{\alpha i}\partial_i)f_{\alpha} + \frac{\Delta t^2}{2}(\partial_t + c_{\alpha i}\partial_i)^2 f_{\alpha} + O(\Delta t^3) = -\frac{\Delta t}{\tau} f_{\alpha}^{neq}.
\end{equation}
Leaving higher orders aside one finds that this is actually a slow mode expansion of $f_{\alpha}$.
Meaning that $f_{\alpha}$ changes only with macroscopic time scales, if this is not ensured higher orders needs to be considered.
Subtracting $\Delta t/2 (\partial_t + c_{\alpha i}\partial_i)$ from both sides yields
\begin{equation}\label{eq:derive_lbm_orders}
    \Delta t (\partial_t + c_{\alpha i}\partial_i)f_{\alpha} = -\frac{\Delta t}{\tau} f_{\alpha}^{neq} + \Delta t (\partial_t + c_{\alpha i}\partial_i)\frac{\Delta t}{2\tau} f^{neq}_{\alpha},
\end{equation}
which is first order in derivatives.
The time and especially the time derivatives need also to be expanded in orders of $Kn$ and therefore
\begin{equation}\label{eq:expansion_time}
    \Delta t \partial_t f_{\alpha} = \Delta t (\epsilon\partial_t^{(1)} + \epsilon^2\partial_t^{(2)} + O(\epsilon^3)) f_{\alpha}.
\end{equation}
For the spatial deviates it is sufficient to use
\begin{equation}\label{eq:expansion_space}
    \Delta t c_{\alpha i}\partial_i f_{\alpha} = \Delta t(\epsilon c_{\alpha i}\partial_i^{(1)}) f_{\alpha}.
\end{equation}
With a note of caution for Eq.~(\ref{eq:expansion_time}) as only the sum of all orders in $\epsilon$ resembles the real time derivative.
Applying both expansions Eq.~(\ref{eq:expansion_f}) and Eq.~(\ref{eq:expansion_time}) to Eq.~(\ref{eq:derive_lbm_orders}) we have
\begin{equation}\label{eq:first_order_esp}
    (\partial_t^{1} + c_{\alpha i}\partial_{i}) f_{\alpha}^{eq} = -\frac{\Delta t}{\tau} f_{\alpha}^{(1)}
\end{equation}
at first order in $\epsilon$ and 
\begin{equation}\label{eq:sec_order_esp}
    \partial_t^{2} f_{\alpha}^{eq} + (\partial_t^{1} + c_{\alpha i}\partial_{i})\left(1 - \frac{\Delta t}{2\tau}\right) f_{\alpha}^{(1)} = -\frac{\Delta t}{\tau} f_{\alpha}^{(2)},
\end{equation}
for $O(\epsilon^2)$.

@@

Taking the moments of Eq.~(\ref{eq:sec_order_esp}) we have
\begin{align}
    \partial_t^{(2)}\rho &= 0, \\
    \partial_t^{(2)}(\rho u_i) + \partial^{(1)}_j\left(1 - \frac{\Delta t}{2\tau}\right)\Pi_{i j}^{(1)} &= 0.
\end{align}
As there is now an equation for $\Pi^{(1)}_{i j}$ it is possible to collect the mass and momentum equation for both $O(\epsilon)$ and $O(\epsilon^2)$
\begin{align}
    (\epsilon\partial_t^{(1)} + \epsilon^2\partial^{(2)})\rho + \epsilon\partial_i^{(1)}(\rho u_i) &= 0, \\
    (\epsilon\partial_t^{(1)} + \epsilon^2\partial^{(2)})(\rho u_i) + \epsilon\partial_j^{(1)}\Pi^{eq}_{i j} &= -\epsilon^2\partial_j^{(2)}\left(1 - \frac{\Delta t}{2\tau}\right) \Pi^{(1)}_{i j}. 
\end{align}
This system in fact resembles the Navier-Stokes with the small pitfall that the viscous stress tensor
\begin{equation}
    \sigma = - \left(1 - \frac{\Delta t}{2\tau}\right) \Pi^{(1)},
\end{equation}
is as of now still unknown.
Cut the last part short for an isothermal equation of state and $f^{eq}$ as function of $O(u^2)$ for example
\begin{equation}\label{eq:eqi_dist1}
    f_{\alpha}^{eq} = \rho(a + b c_{\alpha i} u_i + d (c_{\alpha i} u_i)^2 + e u^2),
\end{equation}
then the tensor is given as
\begin{equation}
    \Pi^{(1)} = -\rho c_s^2\tau(\partial_j^{(1)}u_i + \partial_i^{(1)}u_j) + \tau\partial_k^{(1)}(\rho u_i u_j u_k),
\end{equation}
which concludes the expansion part.
So far however no assumptions on the lattice distributions are made and the equilibrium distribution function has not been specified.
Paving work by He and Luo as well as group theoretical arguments derived by Rubinstein and Luo showed that based on dimensionallity just a few (discrete) velocities are sufficient~\cite{PhysRevE.56.6811, rubinstein2008theory}.
In fact in Chap.~\ref{chapter:first_paper} all numerical experiments were performed on a D2Q9 lattice therefore $\mathbf{c}_{\alpha}$ is
\begin{equation}\label{eq:speeds_method}
\mathbf{c}_{\alpha}  =
\left\{
\begin{array}{ll}
(0,0) & \alpha = 0 \\
\left[\cos{\frac{(\alpha-1)\pi}{4}}, \sin{\frac{(\alpha-1)\pi}{4}} \right] &  \alpha=1,3,5,7 \\
\sqrt{2}\left[\cos{\frac{(\alpha-1)\pi}{4}}, \sin{\frac{(\alpha-1)\pi}{4}} \right] & \alpha=2,4,6,8
\end{array}
\right.,
\end{equation}
The only missing pieces are $a, b, c, d$ of Eq.~(\ref{eq:eqi_dist1}).
Using the set of equations~(\ref{eq:moments_equilibria_1}-\ref{eq:moments_equilibria_4}) one quickly finds
\begin{equation}
    a = 1,\quad b = \frac{1}{c_s^2},\quad d = \frac{1}{2c_s^4},\quad e = \frac{1}{2c_s^2},
\end{equation}
however with the addition of lattice weights to ensure the H-theorem~\cite{krueger2017}
\begin{equation}\label{eq:weightsD2Q9_meth}
w_{\alpha} = \begin{cases}
4/9 &\text{$\alpha = 0$}\\
1/9 &\text{$\alpha = 1,2,3,4$}\\
1/36 &\text{$\alpha = 5,6,7,8$}
\end{cases}
,
\end{equation}
such that the equilibria can be written as
\begin{equation}\label{eq:eqi_dist2}
    f_{\alpha}^{eq} = w_{\alpha}\rho\left(1 + \frac{c_{\alpha i} u_i}{c_s^2} +  \frac{(c_{\alpha i} u_i)^2}{2c_s^4} + \frac{u^2}{2c_s}\right).
\end{equation}
Together with the evolution equation Eq.~(\ref{eq:LBM_discret_noforces}) it is therefore possible to approximate the Navier-Stokes, at least in regimes of small Knudsen and Mach numbers, $Kn = Ma \ll 1$.

>>>>

Coming up in this chapter is a short overview of numerical methods to simulate the thin film equation.
Starting with the straightforward finite differences approach and an introduction of the CFL criteria.
But also introducing the bottom up approach where Newtons equation of motion is solved for every molecule.
Followed by an short introduction to the main method of this work, the lattice Boltzmann method~\cite{PhysRevLett.56.1505, krugerLatticeBoltzmannMethod2017, succi}. 
The mathematical framework as well as it's link to kinetic theory will be discussed and the idea of the Chapmann-Enskog expansion will be outlined~\cite{Chapman, Enskog}. 
Based on the mathematical model it is possible to define a numerical approach.
Using assumptions, mainly concerning the collision operator, the resulting algorithm is fairly easy to implement and shows good scalability.
Which closes the loop with the above statement that the resulting source code is a perfect candidate for GPU programming.

@@

\section{The Lattice Boltzmann Method}\label{sec:LBM}
\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{graphics/Scales_problem.pdf}
    \caption{Schematic display of how different approaches relate to different length and time scales.
    The finer the system is resolved the more computing resources are needed.}
    \label{fig:scales_dummy}
\end{figure}
The lattice Boltzmann method is as the name suggests a discretization approach to the Boltzmann equation~\cite{krugerLatticeBoltzmannMethod2017, succi, wolf-gladrow}.
Boltzmann more then a hundred years ago introduced a model that was build on the assumptions that atoms and molecules move classically.
This was actually just a small portion of his groundbreaking work which forms a whole subsection of physics called statistical mechanics. 
He as well knew that there are a lot of oxygen, nitrogen and other atoms that make up the content of air we inhale with a single breath.
In 1811 already Avogadro calculated that rough number of molecules and around fifty years later Loschmidt came to a similar result~\cite{avogadro1811essai, loschmidt52grosse}
\begin{equation}
    n = \frac{p N_A}{R T},
\end{equation}
where $n$ is the number density, $p$ the pressure, $R$ the gas constant and $T$ the temperature.
The constant named after Avogadro ($N_A$) states that a mole of some substance has about $6 \cdot 10^{23}$ atoms.
Boltzmanns ingenious idea, this adjective is justified as even mathematicians find statistical mechanics appealing, to solve the dynamics of this complex coupled system was to use an statistical ansatz.
Instead of solving the equations of motion for every particle, which is the idea of molecular dynamics as introduced above, Boltzmann decided to introduce distribution functions $f(\mathbf{x},{\boldsymbol\xi},t)$, which depend on position, momentum and time and generate an ensemble.
Figure~\ref{fig:scales_dummy} illustrates the idea coming from either a macroscopic system or a microscopic system.
Instead of dealing with every atom or molecule, which is displayed in the bottom left of the figure, it is also possible to use a more coarse approach. 
Which is shown in the middle of the figure where distributions over ensembles of particles are used~\cite{raabe2004overview}.
Therefore instead of working in the microscopic world the lattice Boltzmann method works in a mesoscopic regime.
Making it computationally more efficient for larger class of problems.
Of course, it is also possible to use a coarser approach and in fact a lot of the classical Navier-Stokes solvers operate in the upper right of Fig.~\ref{fig:scales_dummy}, see Chap.~\ref{chapter:fourth_paper} for some example solvers.

\subsection{The Boltzmann equation}
The dynamics of this distributions $f$ can be formalized and put into an evolution equation which is called the Boltzmann equation
\begin{equation}\label{eq:boltzmann_eq}
    \partial_t f + {\boldsymbol\xi}\cdot\nabla f + \frac{1}{\rho}\mathbf{F}\cdot\partial_{{\boldsymbol\xi}}f = \Omega(f), 
\end{equation}
where ${\boldsymbol\xi}$ is the momentum and the first two terms describe the advection of the distribution due to the atoms and the third term measures the effect of a force $\mathbf{F}$ on the momentum~\cite{krugerLatticeBoltzmannMethod2017}.
On the right side of the equation is an arbitrary complex term, the collision operator.
This operator accounts for all collisions the atoms or particles perform at any given instance of time.
In principle this operator can not be computed analytically, because one need to integrate out the whole phase space $(\int \diff^3\mathbf{x}, \int \diff^3\xi)$ for all possible collision terms, therefore for the two up to n-point interactions.

However with a smart ansatz it is possible to find a suitable approximation to the collision operator.
The easiest ansatz one can make is
\begin{enumerate}
    \item The fluids state is not far of its equilibrium.
    \item During the collision it approaches its equilibrium with a relaxation time $\tau$.
\end{enumerate}
Bhatnagar, Gross and Krook (BGK) were the first ones who worked out the mathematical model behind this ansatz~\cite{PhysRev.94.511}.
This model can be formalized quite simply and reads
\begin{equation}
    \Omega(f) = -\frac{1}{\tau}(f - f^{eq}),
\end{equation}
where $f^{eq}$ denotes the equilibrium distribution function.
The moments of the BGK collision operator satisfy the following set of equations
\begin{align}
    \int \Omega(f) \diff^3\xi = 0, \label{eq:BGK_1}\\
    \int {\boldsymbol\xi}\Omega(f) \diff^3\xi = \mathbf{0}, \label{eq:BGK_2}\\
    \int |{\boldsymbol\xi}|^2\Omega(f) \diff^3\xi = 0, \label{eq:BGK_3}\\
    \int |\mathbf{v}|^2\Omega(f) \diff^3\xi = 0. \label{eq:BGK_4}
\end{align}
The first of the above equations states that the mass is conserved, while Eq.~(\ref{eq:BGK_2}) ensures momentum conservation.
Eqs.~(\ref{eq:BGK_3}, \ref{eq:BGK_4}) tell us that both that the total energy as well as the internal energy are conserved.
Taking this four constraints into consideration as well as the points 1. and 2. one finds that the BGK operator is the simplest one to satisfy them all.
With one side note however, the full collision operator from Boltzmann does predict a different Prandtl number ($Pr$) than the BGK yields.
The Prandtl number $Pr = \nu/\alpha$ measures viscosity against thermal diffusivity ($\alpha$). 
Using BGK one gets $Pr=1$ while monoatomic gases or Boltzmann's operator showing $Pr\simeq 2/3$~\cite{cercignani1988boltzmann, krugerLatticeBoltzmannMethod2017}.

@@

Performing a Taylor expansion of Eq.~(\ref{eq:boltzmann_eq}) with a discrete set of velocities assuming no force is present yields~\cite{krugerLatticeBoltzmannMethod2017}
\begin{equation}\label{eq:Taylor_discret_boltzmann}
    \Delta t (\partial_t + c_{\alpha i}\partial_i)f_{\alpha} + \frac{\Delta t^2}{2}(\partial_t + c_{\alpha i}\partial_i)^2 f_{\alpha} + O(\Delta t^3) = -\frac{\Delta t}{\tau} f_{\alpha}^{neq}.
\end{equation}
Leaving higher orders aside one finds that this is actually a slow mode expansion of $f_{\alpha}$.
Meaning that $f_{\alpha}$ changes only with macroscopic time scales, if this is not ensured higher orders needs to be considered.
Subtracting $\Delta t/2 (\partial_t + c_{\alpha i}\partial_i)$ from both sides yields
\begin{equation}\label{eq:derive_lbm_orders}
    \Delta t (\partial_t + c_{\alpha i}\partial_i)f_{\alpha} = -\frac{\Delta t}{\tau} f_{\alpha}^{neq} + \Delta t (\partial_t + c_{\alpha i}\partial_i)\frac{\Delta t}{2\tau} f^{neq}_{\alpha},
\end{equation}
which is first order in derivatives.
The time and especially the time derivatives need also to be expanded in orders of $Kn$ and therefore
\begin{equation}\label{eq:expansion_time}
    \Delta t \partial_t f_{\alpha} = \Delta t (\epsilon\partial_t^{(1)} + \epsilon^2\partial_t^{(2)} + O(\epsilon^3)) f_{\alpha}.
\end{equation}
For the spatial deviates it is sufficient to use
\begin{equation}\label{eq:expansion_space}
    \Delta t c_{\alpha i}\partial_i f_{\alpha} = \Delta t(\epsilon c_{\alpha i}\partial_i^{(1)}) f_{\alpha}.
\end{equation}
With a note of caution for Eq.~(\ref{eq:expansion_time}) as only the sum of all orders in $\epsilon$ resembles the real time derivative.
Applying both expansions Eq.~(\ref{eq:expansion_f}) and Eq.~(\ref{eq:expansion_time}) to Eq.~(\ref{eq:derive_lbm_orders}) we have
\begin{equation}\label{eq:first_order_esp}
    (\partial_t^{1} + c_{\alpha i}\partial_{i}) f_{\alpha}^{eq} = -\frac{\Delta t}{\tau} f_{\alpha}^{(1)}
\end{equation}
at first order in $\epsilon$ and 
\begin{equation}\label{eq:sec_order_esp}
    \partial_t^{2} f_{\alpha}^{eq} + (\partial_t^{1} + c_{\alpha i}\partial_{i})\left(1 - \frac{\Delta t}{2\tau}\right) f_{\alpha}^{(1)} = -\frac{\Delta t}{\tau} f_{\alpha}^{(2)},
\end{equation}
for $O(\epsilon^2)$.

@@

Taking the moments of Eq.~(\ref{eq:sec_order_esp}) we have
\begin{align}
    \partial_t^{(2)}\rho &= 0, \\
    \partial_t^{(2)}(\rho u_i) + \partial^{(1)}_j\left(1 - \frac{\Delta t}{2\tau}\right)\Pi_{i j}^{(1)} &= 0.
\end{align}
As there is now an equation for $\Pi^{(1)}_{i j}$ it is possible to collect the mass and momentum equation for both $O(\epsilon)$ and $O(\epsilon^2)$
\begin{align}
    (\epsilon\partial_t^{(1)} + \epsilon^2\partial^{(2)})\rho + \epsilon\partial_i^{(1)}(\rho u_i) &= 0, \\
    (\epsilon\partial_t^{(1)} + \epsilon^2\partial^{(2)})(\rho u_i) + \epsilon\partial_j^{(1)}\Pi^{eq}_{i j} &= -\epsilon^2\partial_j^{(2)}\left(1 - \frac{\Delta t}{2\tau}\right) \Pi^{(1)}_{i j}. 
\end{align}
This system in fact resembles the Navier-Stokes with the small pitfall that the viscous stress tensor
\begin{equation}
    \sigma = - \left(1 - \frac{\Delta t}{2\tau}\right) \Pi^{(1)},
\end{equation}
is as of now still unknown.
Cut the last part short for an isothermal equation of state and $f^{eq}$ as function of $O(u^2)$ for example
\begin{equation}\label{eq:eqi_dist1}
    f_{\alpha}^{eq} = \rho(a + b c_{\alpha i} u_i + d (c_{\alpha i} u_i)^2 + e u^2),
\end{equation}
then the tensor is given as
\begin{equation}
    \Pi^{(1)} = -\rho c_s^2\tau(\partial_j^{(1)}u_i + \partial_i^{(1)}u_j) + \tau\partial_k^{(1)}(\rho u_i u_j u_k),
\end{equation}
which concludes the expansion part.
So far however no assumptions on the lattice distributions are made and the equilibrium distribution function has not been specified.
Paving work by He and Luo as well as group theoretical arguments derived by Rubinstein and Luo showed that based on dimensionallity just a few (discrete) velocities are sufficient~\cite{heTheoryLatticeBoltzmann1997, rubinstein2008theory}.
In fact in Chap.~\ref{chapter:first_paper} all numerical experiments were performed on a D2Q9 lattice therefore $\mathbf{c}_{\alpha}$ is
\begin{equation}\label{eq:speeds_method}
\mathbf{c}_{\alpha}  =
\left\{
\begin{array}{ll}
(0,0) & \alpha = 0 \\
\left[\cos{\frac{(\alpha-1)\pi}{4}}, \sin{\frac{(\alpha-1)\pi}{4}} \right] &  \alpha=1,3,5,7 \\
\sqrt{2}\left[\cos{\frac{(\alpha-1)\pi}{4}}, \sin{\frac{(\alpha-1)\pi}{4}} \right] & \alpha=2,4,6,8
\end{array}
\right.,
\end{equation}
The only missing pieces are $a, b, c, d$ of Eq.~(\ref{eq:eqi_dist1}).
Using the set of equations~(\ref{eq:moments_equilibria_1}-\ref{eq:moments_equilibria_4}) one quickly finds
\begin{equation}
    a = 1,\quad b = \frac{1}{c_s^2},\quad d = \frac{1}{2c_s^4},\quad e = \frac{1}{2c_s^2},
\end{equation}
however with the addition of lattice weights to ensure the H-theorem~\cite{krugerLatticeBoltzmannMethod2017}
\begin{equation}\label{eq:weightsD2Q9_meth}
w_{\alpha} = \begin{cases}
4/9 &\text{$\alpha = 0$}\\
1/9 &\text{$\alpha = 1,2,3,4$}\\
1/36 &\text{$\alpha = 5,6,7,8$}
\end{cases}
,
\end{equation}
such that the equilibria can be written as
\begin{equation}\label{eq:eqi_dist2}
    f_{\alpha}^{eq} = w_{\alpha}\rho\left(1 + \frac{c_{\alpha i} u_i}{c_s^2} +  \frac{(c_{\alpha i} u_i)^2}{2c_s^4} + \frac{u^2}{2c_s}\right).
\end{equation}
Together with the evolution equation Eq.~(\ref{eq:LBM_discret_noforces}) it is therefore possible to approximate the Navier-Stokes, at least in regimes of small Knudsen and Mach numbers, $Kn = Ma \ll 1$.
